Example script the `dispRity` paper

### 2018-03-01 paper/dispRity_paper.tex
fixed time.subsets to chrono.subsets in paper

This splitting can be done using the \texttt{custom.subsets} or \texttt{time.subsets} functions.
The first argument is the matrix defining the space and a list of elements to group into different subsets.
The second also takes a matrix and arguments giving the age of the taxa (a dated phylogeny of the elements present in the morphospace - see below) and which subsets to create: (1) discrete time subsets (or time-binning) or (2) continuous time subsets (or time-slicing).

@@

\noindent \texttt{> time\_subsets <- time.subsets(data = BeckLee\_mat50, tree = BeckLee\_tree,}\\ \texttt{time = time\_bins, method = \textquotedbl discrete\textquotedbl)}\\
\noindent \texttt{> bootstraps2 <- boot.matrix(time\_subsets)}\\
\noindent \texttt{> disparity4 <- dispRity(bootstraps2, metric = c(sum, variances))}\\

>>>>

This splitting can be done using the \texttt{custom.subsets} or \texttt{chrono.subsets} functions.
The first argument is the matrix defining the space and a list of elements to group into different subsets.
The second also takes a matrix and arguments giving the age of the taxa (a dated phylogeny of the elements present in the morphospace - see below) and which subsets to create: (1) discrete time subsets (or time-binning) or (2) continuous time subsets (or time-slicing).

@@

\noindent \texttt{> time\_subsets <- chrono.subsets(data = BeckLee\_mat50, tree = BeckLee\_tree,}\\ \texttt{time = time\_bins, method = \textquotedbl discrete\textquotedbl)}\\
\noindent \texttt{> bootstraps2 <- boot.matrix(time\_subsets)}\\
\noindent \texttt{> disparity4 <- dispRity(bootstraps2, metric = c(sum, variances))}\\
